Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-03 cikm2016/futurework.tex
Future Work tidying

In this paper, we have considered the parsing of strings, but dates are often formatted as integers (\eg \texttt{201507016}). It is significantly faster to decompose integers into date parts using arithmetic operations (\eg \texttt{mod} and \texttt{div}) than by using locale-sensitive string parsing functions. Timestamp preparation from numeric representations is another form of preparation which we would like to automate.

>>>>

In this paper, we have considered the parsing of strings, but dates are often formatted as integers (\eg \functionname{201507016}). 
It is significantly faster to decompose integers into date parts using arithmetic operations (\eg \texttt{mod} and \texttt{div}) than by using locale-sensitive string parsing functions. 
Timestamp preparation from numeric representations is a related task that we would also like to automate.
